---
title       : Week4 Assignment 
subtitle    : Developing Data Product
author      : Yuji.H
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : draft # {standalone, draft}
knit        : slidify::knit2slides
---

## Probability distribution
In statistics, a probability distribution assigns a probability to each measurable 
subset of the possible outcomes of a random experiment.

My application enable us to visualize following probability distribution.


- Normal distribution
- Uniform distribution
- poisson distribution
- Gamma distribution
- Exponential distribution


---
##  ui.R

- Input :t1(select input : "normal","exponential","poisson","gamma","uniform")
- Inpput:s1(sliderinput,  decide sample size)
- Output:p1(renderplot of selected probability distribution)
- Output:v1(length of samples, basics statistics)


---

## server.R(1)

- Rely on input t1, different histogram is illustrated.

```{r, eval=FALSE, echo=TRUE}

   if(input$t1 == "normal"){
      samples<<-rnorm(input$s1)
      hist(samples)}     ## Normal Distribution
   if(input$t1 == "exponential"){
      samples<<-rexp(input$s1,5)
      hist(samples)   }  ## Exponential Distribution
   if(input$t1 == "poisson"){
      samples<<-rpois(input$s1,5)
      hist(samples)   }  ## Poissoon Distribution
   if(input$t1 == "gamma"){
      samples<<- rgamma(input$s1,shape=10,scale=1/5)
      hist(samples)   }  ## Gamma Distribution
   if(input$t1=="uniform"){ 
      samples<<-runif(input$s1)
      hist(samples)}     ## Uniform Distribution
```


---

## server.R(2)

- Basic statistical quantities of selected distribution are displayed under histogram.


```{r,echo=TRUE, eval=FALSE}
    output$v1<-renderPrint({
    input$s1;print(length(samples));summary(samples)})
}








